### 2014-10-15 fundamentals/intro.tex
more intro

As nuclear power expands both domestically and internationally, nuclear fuel cycle
performance analysis on technical, economic, political, and environmental axes increases 
in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear, 
chemical, industrial, and political phenomena. Nuclear fuel cycle simulators 
therefore couple complex systems such as nuclear process physics, 
facility deployment, and material routing. However, most nuclear fuel cycle 
simulators have not incorporated modern insights in simulation science and 
software architecture that can enable more efficient, accurate, robust, and 
validated analysis. The Cyclus Nuclear Fuel Cycle Simulator Framework and 
its modeling ecosystem answer the need for a next generation nuclear fuel cycle 
simulator.

@@

Simulators drive \gls{RDD} by calculating metrics that can be compared among fuel 
cycles. Examples include measures of economic feasibility (i.e., \gls{LCOE}), 
proliferation risk (i.e., total separated Pu), and environmental performance 
(i.e., waste volume).

Methods for calculating those metrics vary among simulators. Some model the 
fuel cycle at static equillibrium, while others capture fuel cycle dynamics.  
Similarly, while some simulators discretely model material and and facilities, 
others track streams of materials and fleets of facilities in an aggregated 
fashion. Depending on their intended use, simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail. For this reason, 
some simulators specialize in economics, material isotopics, or transmutation 
detail, where others do not.

Historically, the national laboratories have driven development and regulated 
the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{modeling_yacout_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}, while universities and industry have 
simultaneously developed tools of their own as well, such as 
\gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi}.

>>>>

As nuclear power expands both domestically and internationally, nuclear fuel cycle
performance analysis on technical, economic, political, and environmental axes increases 
in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear, 
chemical, industrial, and political phenomena. Nuclear fuel cycle simulators 
therefore couple complex systems such as nuclear process physics, 
facility deployment, and material routing. However, most nuclear fuel cycle 
simulators have not incorporated modern insights in simulation science and 
software architecture that can enable more efficient, accurate, robust, and 
validated analysis.

The \Cyclus Nuclear Fuel Cycle Simulator framework and 
its modeling ecosystem answer this need for a next generation nuclear fuel cycle 
simulator. Dynamic simulation of nuclear fuel cycles with discrete agents 
and up to isotopic resolution support 
levels of detail appropriate for a varied community of analysts
interested in a range of analysis types. Additionally \Cyclus employs an 
open development process that supports user access and 
encourages developer extensions.

@@

Nuclear fuel cycle simulators can drive \gls{RDD} by calculating `metrics', 
quantitative measures of performance that 
can be compared among fuel cycle options. The feasibility of technology 
strategies, dynamics of transitions between fuel cycles, and many other 
measures of performance can be expressed in terms of these metrics. For example, 
economic feasibility is often measured in \gls{LCOE} while proliferation risk 
can be proportional to total kilograms of separated Pu, and environmental 
performance might be measured in spent fuel volume, toxicity, or mined uranium.

Methods for calculating those metrics vary among simulators. Some model the 
system of facilities, economics, and materials at static equillibrium, while 
others capture its dynamics.  
Similarly, while some simulators discretely model material and facilities, 
others treat materials in streams and facilities in fleets, in an aggregated 
fashion. Depending on their intended use, simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail while neglecting 
others. A simulator created for policy modeling might have excellent 
capability in economics while material isotopics and transmutation detail are 
neglected.

Historically, the national laboratories have driven development and regulated 
the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{modeling_yacout_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}. With limited access to those tools, 
universities and industry have simultaneously developed tools of their own, 
such as \gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi}.
